### 2016-12-03 real/draft.tex
[draft] [references] update asymptotic approximation

%% CHANGE THIS DATE AS YOU MODIFY THE FILE
\newcommand{\vdate}{161202}
\pagestyle{myheadings}
\markboth{Version \vdate} {Version \vdate}

@@

First, the parameter $\lambda$ is eliminated as follows. The number of
packets $N$ is Poisson-distributed
\begin{align}
  \lleq{caa}
  p(N\cond\lambda) &= \frac{e^{-\lambda}\lambda^{N}}{N!}
  \quad N = 0,1,\ldots,\infty.
\end{align}
Data $n$ is naturally presumed to have arisen from the same Poisson
distribution with the same $\lambda$, so $p(n\cond\lambda) =
e^{-\lambda}\lambda^{n}/n!$. %
% and since $n$ is just one realisation of $N$, it likewise is
% poissonian $p(n\cond\lambda) = e^{-\lambda}\lambda^{n}/n!$ with the
% same $\lambda$.
The posterior for $\lambda$ is found from the data $n$ via Bayes'
Theorem,
\begin{align}
  \lleq{pmd}
  p(\lambda\cond n) %
  &= \frac{p(n\cond\lambda)\,p(\lambda)} {p(n)}
  \ =\ \frac{p(n\cond\lambda)\,p(\lambda)} %
  {\int \rmdx{\lambda} p(n\cond\lambda)\,p(\lambda)} \,.
\end{align}
We use an improper prior 
\begin{align}
  \lleq{pmf}
  p(\lambda) = c \lambda^{-a},
\end{align}
meaning that $\int_0^\infty d\lambda\,p(\lambda)$ is known only up to
a constant $c$. A hyperparameter choice $a=0$ yields the uniform
prior, $a=1/2$ gives the Jeffreys and reference prior, and $a=1$ is
the transformation-group result advocated by
Jaynes~\cite[Ch. 12]{jaynes2003probability}. An improper prior is not
a problem because $c$ cancels out when calculating the posterior,
provided that $n \ge 1$; i.e., at least one packet is observed in the
bin.\footnote{For a uniform prior, the case $a{=}0$, we require of
  course a parameter $\lambda_{\rm max}$. As long as
  $\lambda_{\rm max}$ is large enough, it too would cancel.}, The
posterior is
\begin{align}
  \lleq{pms}
  p(\lambda\cond n) 
  &= \GammaDist(\lambda \cond \alpha = n{-}a{+}1 \,,\, \beta = 1)\,,
\end{align}
where the $\GammaDist$ distribution with shape parameter $\alpha > 0$ and
rate parameter $\beta > 0$ is defined as
\begin{align}
  \lleq{gma}
  \GammaDist(x\cond \alpha, \beta) 
  &= \frac{\beta^\alpha}{\Gamma(\alpha)} x^{\alpha-1} e^{-\beta x}\,,
  \quad 0 \leq x < \infty.
\end{align}
The evidence is 
$p(n) =  \int_0^\infty d\lambda\, p(n\cond\lambda)\,p(\lambda) = c\,(n-a)!/n!$
% \begin{align}
%   \lleq{pmg}
%   p(n) 
%   &=  \int_0^\infty d\lambda\, p(n\cond\lambda)\,p(\lambda)
%     \ =\ c\frac{(n-a)!}{n!} \,, \\
% \end{align}
and inserting Eqs.~(\ref{caa}) and (\ref{pmd}), the prediction for $N$
given $n$ is
\begin{align}
  \lleq{pmh}
  p(N\cond n) %
  &= \int_0^\infty d\lambda\, p(N\cond\lambda)\,p(\lambda\cond n)
  \ =\ \frac{(N+n-a)!}{N!\,(n-a)!\,2^{N+n+1-a}} \, .
\end{align}
so that Eq.~(\ref{sll}) simplifies to
\begin{align}
  \lleq{gmh}
  p(Q\cond n,\bml)
  &= \sum_{N=0}^\infty \;
    p(N\cond n)\;
    \int d\bmL\;
    p(Q\cond N,\bmL)\;
    \int d\bmphi\;
    p(\bmL\cond N,\bmphi)\,
    p(\bmphi\cond n,\bml),
\end{align}

@@

We return to the general formulation of \refeq{sll}, whose factors we 
rearrange to write it as 

@@

with $p(\bmL\cond n,\bmphi) = \prod_{j=1}^n p(L\cond\bmphi)$ as
before.  If, as assumed, $p(N\cond\lambda)$ is Poissonian, there is a
simple relation between their respective moments\footnote{The $k$-th
  moment of a variable is defined as
  $\mu_k = \expect{x^k} = \int dx\,p(x)\,x^k, k = 1,2,\ldots$, while
  the variance is equal to $\sigma^2 = \mu_2 - \mu_1^2$.} %
for $p(Q\cond \lambda,\bmphi)$ and $p(L\cond \bmphi)$ as follows.
\fred{citation} %
In terms of the moments and variance of $L$,

@@

  \mu_1 &\equiv \expect{\Lum}, \qquad 

@@

  = \expect{\Lum^2} - \expect{\Lum}^2\,,

@@

the first moment and variance of $Q$ are 

@@

  \expect{Q} = \lambda\, \mu_1, \qquad 
  \variance{Q} = \lambda \mu_2 = \lambda (\mu_1^2 + \sigma^2) \,.

@@

for \textit{any} $p(L\cond\bmphi)$. 

@@

\hans{Stopped editing HERE 161202 18h30}

@@

From Theorem 4.3.1 of \cite{bening2002generalized}, we can conclude

@@

@@

  P(\Lumtot \cond \bmphi) 

@@

    = \GaussianDist \left( \Lumtot \cond \lambda \mu, \lambda (\mu^2 + \sigma^2) \right).

@@

This result is a drastic simplification as it eliminates both the sum
over $N$ in \refeq{qab} and the integral over $\bmL$ in \refeq{qaf}.
That allows us to model $\Lumtot$ in each bin \emph{without} making
concrete assumptions about the functional form of
$P(\Lum \cond \bmphi)$; i.e., we may now view $\bmphi$ as the
collection of first and second moments in each bin in addition to
$\lambda$. Continuing the notation of \refeq{qadd},

@@

  \bmphi =  \left(\lambda_b, \mu_b, \sigma^2_b \right)_{b=1}^B.

@@

although the actual frequencies may be quite different from a

@@

knowledge \emph{before} observing $\bmy$ well. To make the
calculations easier, we assume a conjugate prior for unknown $\mu$ and
$\sigma^2$. The standard result for the posterior is

@@

  p(\mu, \sigma^2 \cond \bmy) &= \GaussianDist(\mu \cond \mu_0^\prime, \frac{\sigma^2}{n_0^\prime}) \InvGammaDist\left( \sigma^2 \cond \frac{\nu_0^\prime}{2}, \frac{\nu_0^\prime \sigma_0^{\prime 2}}{2} \right)

@@

where the hyperparameters are updated from prior to posterior based on $\bmy$ as

@@

  \lleq{rag}
  \expectest{\lum} &= \frac{1}{n} \sum_{i=1}^n \lum_i,\\
  \lleq{rah}  n_0^\prime &= n_0 + n,\\
  \lleq{rai}    \mu_0^\prime &= \frac{n_0 \mu_0 + n \expectest{\lum}}{n^\prime},\\
  \lleq{raj}    \nu_0^\prime &= \nu_0 + n,\\
  \lleq{rak}    \nu_0^\prime \sigma_0^{\prime 2} &= \nu_0 \sigma_0^{ 2} + \sum_{i=1}^n \left(\lum_j - \expectest{\lum}\right)^2 + \frac{n_0 n}{n^\prime} \left(\mu_0 - \expectest{\lum}\right)\,.

@@

@@

  $n_0 = \mu_0 = \nu_0 = 0$, so the value $\sigma_0^2>0$ is
  irrelevant.

@@

  Finally all ingredients for the prediction of $\Lumtot$ in one bin are
  ready, and \refeq{qaa} simplifies to
\begin{align}
  \lleq{ral}
  p(\Lumtot \cond \bmy) &= \int \rmdx{\lambda} \rmdx{\mu} \rmdx{\sigma^2} \GaussianDist \left( \Lumtot \cond \lambda \mu, \lambda \sigma^2 \right) p(\lambda \cond \bmy) p( \mu, \sigma^2 \cond \bmy) \,,
\end{align}
where $ p(\lambda \cond \bmy)$ is given by \refeq{pms} and
$ p( \mu, \sigma^2 \cond \bmy)$ by
\refeq{raf}--\refeq{rak}.

@@

Unfortunately we could not integrate \refeq{ral} analytically but
since the integrand is unimodal and strongly peaked the Laplace or
saddle-point approximation~\cite[Ch. 27]{mackay2003information} can be
applied in two ways. First, if only the value
$p(\Lumtot=\lumtot \cond \bmy)$ for some particular $q$ is sought,
then one can approximate it directly. Second, we can compute the
moments of $\Lumtot$ through the \emph{moment-generating
  function}\fredmargin{ref}
\begin{align}
  \lleq{rap}
  M(t \cond \bmy) = \int_0^{\infty} \rmdx{\Lumtot} p(\Lumtot \cond \bmy) e^{-t \Lumtot} \,
\end{align}
from which the moments are accessible by differentiation
\begin{align}
  \lleq{raq}
  \expect{\Lumtot^k} = (-1)^k \eval{\dv[k]{M(t \cond \bmy)}{t}}_{t=0}
\end{align}

Assuming all involved integrals are absolutely convergent, we can
exchange the order of integration and find
\begin{align}
  \lleq{rar}
  M(t \cond \bmy) &= \int \rmdx{\lambda} \rmdx{\mu} \rmdx{\sigma^2} p(\lambda \cond \bmy) p( \mu, \sigma^2 \cond \bmy)  f(t \cond \lambda, \mu, \sigma^2),
  \intertext{where }
  f\left(t \cond  \lambda, \mu, \sigma^2\right) &\equiv \int \rmdx{\Lumtot} \GaussianDist \left( \Lumtot \cond \lambda \mu, \lambda \sigma^2 \right) e^{-t \Lumtot}= \frac{1}{2} e^{t \lambda (t \sigma^2/2 - \mu)} \left[ 1 + \erf\qty( \frac{\sqrt{\lambda}(\mu - t \sigma^2)}{\sqrt{2 \sigma^2}}) \right].
\end{align}
This implies that the mean and variance of $\Lumtot$ require an integral over the three parameters
\begin{align}
  \lleq{ras}
  \expect{\Lumtot} &= \int \rmdx{\lambda} \rmdx{\mu} \rmdx{\sigma^2} p(\lambda \cond \bmy) p( \mu, \sigma^2 \cond \bmy) \qty(-\eval{\dv{f(t \cond  \lambda, \mu, \sigma^2)}{t}}_{t=0})\\
  \variance{\Lumtot} &= \int \rmdx{\lambda} \rmdx{\mu} \rmdx{\sigma^2} p(\lambda \cond \bmy) p( \mu, \sigma^2 \cond \bmy) \qty(\eval{\dv[2]{f(t \cond  \lambda, \mu, \sigma^2)}{t}}_{t=0}) - \expect{\Lumtot}^2
\end{align}
We implemented the above formulae in the julia language~\cite{julia14}
and used Newton's method from the \texttt{Optim.jl} package in
combination with automatic
differentiation~\cite{RevelsLubinPapamarkou2016} to optimize the
respective integrand and compute the Hessian at the mode. As initial
values, we slightly offset the sample estimates to avoid issues if the
optimizer cannot improve on the initial guess and found convergence
within $\order{10}$ steps:
\begin{align}
  \lleq{rat}
  \qty(\lambda, \mu, \sigma^2) = 1.0005 (n, \expectest{\lum}, \widehat{\variance{\lum}}).
\end{align}
\fred{Did we define expectation value and variance? Should be in notation or intro section}
\fred{At least for us, I should do a comparison plot to evaluate $p(\Lumtot \cond \bmy)$ with both methods }
\fred{We need a plot, the one to compare predictions and 250 real replicas or 100 virtual replicas?}
\fred{Advantage of this approach: no need to store all packets anymore, sum and sum of squares can be accumulated online $\Rightarrow$ reduced computation and storage requirements}

@@

@@

>>>>

%% CHANGE THIS DATE AS YOU MODIFY THE FILE
\newcommand{\vdate}{161203}
\pagestyle{myheadings}
\markboth{Version \vdate} {Version \vdate}

@@

First, the parameter $\lambda$ is eliminated as follows. The number of
packets $N$ is Poisson-distributed
\begin{align}
  \lleq{caa}
  p(N\cond\lambda) &= \frac{e^{-\lambda}\lambda^{N}}{N!}
  \quad N = 0,1,\ldots,\infty.
\end{align}
Data $n$ is naturally presumed to have arisen from the same Poisson
distribution with the same $\lambda$, so $p(n\cond\lambda) =
e^{-\lambda}\lambda^{n}/n!$. %
% and since $n$ is just one realisation of $N$, it likewise is
% poissonian $p(n\cond\lambda) = e^{-\lambda}\lambda^{n}/n!$ with the
% same $\lambda$.
The posterior for $\lambda$ is found from the data $n$ via Bayes'
Theorem,
\begin{align}
  \lleq{cab}
  p(\lambda\cond n) %
  &= \frac{p(n\cond\lambda)\,p(\lambda)} {p(n)}
  \ =\ \frac{p(n\cond\lambda)\,p(\lambda)} %
  {\int \rmdx{\lambda} p(n\cond\lambda)\,p(\lambda)} \,.
\end{align}
We use an improper prior 
\begin{align}
  \lleq{pmf}
  p(\lambda) = c \lambda^{-a},
\end{align}
meaning that $\int_0^\infty d\lambda\,p(\lambda)$ is known only up to
a constant $c$. A hyperparameter choice $a=0$ yields the uniform
prior, $a=1/2$ gives the Jeffreys and reference prior, and $a=1$ is
the transformation-group result advocated by
Jaynes~\cite[Ch. 12]{jaynes2003probability}. An improper prior is not
a problem because $c$ cancels out when calculating the posterior,
provided that $n \ge 1$; i.e., at least one packet is observed in the
bin.\footnote{For a uniform prior, the case $a{=}0$, we require of
  course a parameter $\lambda_{\rm max}$. As long as
  $\lambda_{\rm max}$ is large enough, it too would cancel.}, The
posterior is
\begin{align}
  \lleq{pms}
  p(\lambda\cond n) 
  &= \GammaDist(\lambda \cond \alpha = n{-}a{+}1 \,,\, \beta = 1)\,,
\end{align}
where the $\GammaDist$ distribution with shape parameter $\alpha > 0$ and
rate parameter $\beta > 0$ is defined as
\begin{align}
  \lleq{gma}
  \GammaDist(x\cond \alpha, \beta) 
  &= \frac{\beta^\alpha}{\Gamma(\alpha)} x^{\alpha-1} e^{-\beta x}\,,
  \quad 0 \leq x < \infty.
\end{align}
The evidence is 
$p(n) =  \int_0^\infty d\lambda\, p(n\cond\lambda)\,p(\lambda) = c\,(n-a)!/n!$
% \begin{align}
%   \lleq{pmg}
%   p(n) 
%   &=  \int_0^\infty d\lambda\, p(n\cond\lambda)\,p(\lambda)
%     \ =\ c\frac{(n-a)!}{n!} \,, \\
% \end{align}
and inserting Eqs.~(\ref{caa}) and (\ref{cab}), the prediction for $N$
given $n$ is
\begin{align}
  \lleq{pmh}
  p(N\cond n) %
  &= \int_0^\infty d\lambda\, p(N\cond\lambda)\,p(\lambda\cond n)
  \ =\ \frac{(N+n-a)!}{N!\,(n-a)!\,2^{N+n+1-a}} \, .
\end{align}
so that Eq.~(\ref{sll}) simplifies to
\begin{align}
  \lleq{gmh}
  p(Q\cond n,\bml)
  &= \sum_{N=0}^\infty \;
    p(N\cond n)\;
    \int d\bmL\;
    p(Q\cond N,\bmL)\;
    \int d\bmphi\;
    p(\bmL\cond N,\bmphi)\,
    p(\bmphi\cond n,\bml),
\end{align}

@@

\subsection{Derivation of $p(Q\,|\,n,\boldmath{\ell})$ for large $n$}

We return to the general formulation of \refeq{sll} and re-arrange its
factors into

@@

with $p(\bmL\cond n,\bmphi) = \prod_{j=1}^n p(L_j\cond\bmphi)$ as
before. Writing the moments and variance of $L$ as\footnote{The $k$-th
  moment of variable $x$ is defined as the expectation value
  $\mu_k = \expect{x^k} = \int dx\,x^k\,p(x),\; k = 0,1,2,\ldots$.} %

@@

  \mu =  \mu_1 &\equiv \expect{\Lum}, \qquad 

@@

  = \expect{\Lum^2} - \expect{\Lum}^2,

@@

it is easy to show that, for the Poissonian compound process
(\ref{asd}), the first moment and variance of $Q$ are related to those
of $L$ by
%%%%%%%%%%%%%%%%
\fredmargin{citation} %

@@

  \expect{Q} = \lambda \mu, \qquad 
  \variance{Q} = \lambda \mu_2 = \lambda (\mu^2 + \sigma^2) \,.

@@

for any probability $p(L\cond\bmphi)$.

@@

@@

%%%%%%%%%%%
\hans{The variance is the second so-called \textit{cumulant}. The
  relation for all orders is that the $k$-th order cumulant
  $\kappa_q(Q)$ is equal to $\lambda$ times the $k$-th order moment of
  $L$, $\mu_k$. The skewness is therefore
  $\kappa_3(Q)/\kappa_2(Q)^{3/2} = \lambda \mu_3/(\lambda \mu_2)^{3/2}
  = \lambda^{-1/2} \mu_3/\mu_2^{3/2}$. The magnitude of the correction
  to (rab) due to $\kappa_3$ and higher orders is unclear.}
%%%%%%%%%%%
From Theorem 4.3.1 of Ref.~\cite{bening2002generalized}, we conclude

@@

a gaussian or normal distribution,

@@

  P(\Lumtot \cond \lambda,\bmphi) 

@@

    = \GaussianDist \left( \Lumtot \cond \lambda \mu_1, \lambda (\mu^2 {+} \sigma^2) \right).

@@

This drastic simplification eliminates both the sum over $N$ and the
integral over $\bmL$ in \refeq{asd} and allows us to model $\Lumtot$
in each bin without having to make concrete assumptions about the
functional form of $P(\Lum \cond \bmphi)$. Correspondingly, we may now
redefine $\bmphi$ as the moment $\mu$ and variance $\sigma^2$ of
$p(L\cond\bmphi)$,

@@

  \bmphi =  (\mu, \sigma^2).

@@

although the actual data histograms may be quite different from a

@@

knowledge \emph{before} data $\bmy$ is observed. To simplify the
calculations, we assume a conjugate prior for unknown $\mu$ and
$\sigma^2$. The standard result for the posterior is a Gaussian for
$\mu$ and an Inverse Gamma distribution for $\sigma^2$,

@@

  p(\mu, \sigma^2 \cond \bmy) 
  &= \GaussianDist\left(\mu \cond \mu_0^\prime, \sigma^2/n_0^\prime\right) %
    \InvGammaDist\left( \sigma^2 \,\Bigl|\, \tfrac{1}{2}\nu_0^\prime, 
    \tfrac{1}{2}\nu_0^\prime \sigma_0^{\prime 2} \right)

@@

where the hyperparameters $(n_0',\mu_0',\nu_0')$ are updated from
prior to posterior based on $\bmy$ with the sample mean
$\langle\lum\rangle = (1/n) \sum_{j=1}^n \lum_j$,

@@

  %\lleq{rag}
  \lleq{rah}  n_0^\prime 
  &= n_0 + n,\\
  \lleq{rai}    \mu_0^\prime 
  &= \frac{n_0 \mu_0 + n \langle\lum\rangle}{n_0^\prime},\\
  \lleq{raj}    \nu_0^\prime 
  &= \nu_0 + n,\\
  \lleq{rak}    
  \nu_0^\prime \sigma_0^{\prime 2} 
  &= \nu_0 \sigma_0^{ 2} 
    + \sum_{j=1}^n \left(\lum_j - \langle\lum\rangle\right)^2 
    + \frac{n_0 n}{n_0^\prime} \left(\mu_0 - \langle\lum\rangle\right)^2\,.

@@

\hans{H: The last term in (\ref{rak}) was missing a square. Even so, I
  have not yet been able to verify that equation (rak) from
  Wikipedia's Normal Distribution entry agrees with Eq.(200) of
  Murphy's 2007 paper.} %

@@

$n_0 = \mu_0 = \nu_0 = 0$, so the value $\sigma_0^2>0$ is irrelevant.

@@

The above equations also show that the data $\bmy$ appears only in the
form of $n$ and the first two sample moments
$m_1 = \langle\ell\rangle$ and $m_2 = \langle\ell^2\rangle$.
Inserting all these ingredients into Eq.~(\ref{asc}), we obtain
  \lleq{ral}
  p(\Lumtot \cond \bmy) 
  &= \int d\lambda\; d\mu\; d\sigma^2\;
    p(\lambda \cond n)\; p( \mu, \sigma^2 \cond \bmy)\;
    \GaussianDist \left( \Lumtot \cond \lambda \mu, \lambda (\sigma^2{+}\mu^2) \right)
    \,,
where $ p(\lambda \cond n)$ is given by \refeq{pms} and
$ p( \mu, \sigma^2 \cond \bmy)$ by Eqs.~(\ref{raf})--(\ref{rak}).

@@

While the integral in \refeq{ral} cannot be integrated analytically,
the integrand is unimodal and strongly peaked, so that the Laplace or
saddle-point approximation~\cite[Ch. 27]{mackay2003information} can be
applied. If only the value $p(\Lumtot{=}\lumtot \cond n,m_1,m_2)$ at the
total data luminosity $q$ is sought, then one can approximate it
directly. In addition, we can compute the moments of $\Lumtot$ through
the \emph{moment generating function} \cite{stuart1994kendall}
\begin{align}
  \lleq{rap}
  M(t \cond \bmy) = \int_0^{\infty} \rmdx{\Lumtot} p(\Lumtot \cond \bmy) e^{-t \Lumtot} \,
\end{align}
from which the moments are accessible by differentiation
\begin{align}
  \lleq{raq}
  \expect{\Lumtot^k} = (-1)^k \eval{\dv[k]{M(t \cond \bmy)}{t}}_{t=0}
\end{align}
Assuming all involved integrals are absolutely convergent, we can
exchange the order of integration and find
\begin{align}
  \lleq{rar}
  M(t \cond \bmy) &= \int \rmdx{\lambda} \rmdx{\mu} \rmdx{\sigma^2} p(\lambda \cond \bmy) p( \mu, \sigma^2 \cond \bmy)  f(t \cond \lambda, \mu, \sigma^2),
  \intertext{where }
  f\left(t \cond  \lambda, \mu, \sigma^2\right) &\equiv \int \rmdx{\Lumtot} \GaussianDist \left( \Lumtot \cond \lambda \mu, \lambda \sigma^2 \right) e^{-t \Lumtot}= \frac{1}{2} e^{t \lambda (t \sigma^2/2 - \mu)} \left[ 1 + \erf\qty( \frac{\sqrt{\lambda}(\mu - t \sigma^2)}{\sqrt{2 \sigma^2}}) \right].
\end{align}
This implies that the mean and variance of $\Lumtot$ require an integral over the three parameters
\begin{align}
  \lleq{ras}
  \expect{\Lumtot} &= \int \rmdx{\lambda} \rmdx{\mu} \rmdx{\sigma^2} p(\lambda \cond n) p( \mu, \sigma^2 \cond \bmy) \qty(-\eval{\dv{f(t \cond  \lambda, \mu, \sigma^2)}{t}}_{t=0})\\
  \variance{\Lumtot} &= \int \rmdx{\lambda} \rmdx{\mu} \rmdx{\sigma^2} p(\lambda \cond n) p( \mu, \sigma^2 \cond \bmy) \qty(\eval{\dv[2]{f(t \cond  \lambda, \mu, \sigma^2)}{t}}_{t=0}) - \expect{\Lumtot}^2
\end{align}
We implemented the above formulae in the julia language~\cite{julia14}
and used Newton's method from the \texttt{Optim.jl} package in
combination with automatic
differentiation~\cite{RevelsLubinPapamarkou2016} to optimize the
respective integrand and compute the Hessian at the mode. As initial
values, we slightly offset the sample estimates to avoid issues if the
optimizer cannot improve on the initial guess and found convergence
within $\order{10}$ steps:
\begin{align}
  \lleq{rat}
  \qty(\lambda, \mu, \sigma^2) = 1.0005 (n, \langle\lum\rangle, \langle\lum^2\rangle{-}\langle\lum\rangle^2).
\end{align}
\hans{H: If threefold integrals must be carried out for the expectation values, why not do so
for Eq (ral) directly rather than just the expectation values?} %
\fred{Did we define expectation value and variance? Should be in notation or intro section. Hans: see footnote 2.} %
\fred{At least for us, I should do a comparison plot to evaluate $p(\Lumtot \cond \bmy)$ with both methods } %
\fred{We need a plot, the one to compare predictions and 250 real replicas or 100 virtual replicas?} %
\fred{Advantage of this approach: no need to store all packets anymore, sum and sum of squares can be accumulated online $\Rightarrow$ reduced computation and storage requirements}

@@

TODO

@@

\fred{Will be removed later}
